\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      % \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[1]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} \\
    \end{tabular*}\vspace{-5pt} 
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{\Large Wei-Hsiang (Matt) Wang} \\
  \vspace{8px}
  \href{mailto:mattwang44@gmail.com}{\faEnvelope \hspace{1px} mattwang44@gmail.com} {{$\vert$}}
  \href{https://github.com/mattwang44/}{\faGithub \hspace{1px} mattwang44} {{$\vert$}}
  \href{https://www.linkedin.com/in/weihsiang-wang/}{\faLinkedin \hspace{1px} Wei-Hsiang Wang} {{$\vert$}}
  % \href{https://mattwang44.dev/}{ \faPenSquare \hspace{1px} mattwang44.dev} {{$\vert$}}
  { \faPhoneSquare \hspace{1px} +886-988-211-953}
\end{center}

%-----------SUMMARY-----------------
\vspace{-8px}
\section{Summary}
  \begin{itemize}[leftmargin=16px]
    \item\small{{Backend engineer with strong DevOps expertise and hands-on experience architecting cloud infrastructure \vspace{-8pt}}}
    \item\small{{Tech lead delivering scalable distributed systems across domains including computer vision, logistics, and fintech, tailoring architectures to meet evolving product and business needs\vspace{-8pt}}}
    \item\small{{Active contributor \& event organizer in the Taiwanese Python community  \vspace{-8pt}}}
    \resumeItemListEnd
%-----------EXPERIENCE-----------------
\vspace{4pt}
\section{Work Experience}
  \resumeSubHeadingListStart
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{GoFreight} & \textit{Apr 2022 - present} \\
      \multicolumn{2}{l}{\footnotesize GoFreight is a leading vertical SaaS platform for logistics, optimizing freight forwarding operations and boosting overall efficiency.} \\
    \end{tabular*}
    \vspace{0px}
    
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{Senior Backend Engineer \& Tech Lead} & \textit{} \\
    \end{tabular*}
    \vspace{0px}

    \resumeSubSubheading
      {\hspace{8px}Engineering Leadership \& Enablement}
      \resumeItemListStart
        \resumeItem{Spearheaded the launch of microservices and formalized GitOps CI/CD conventions (GitHub Action \& ArgoCD) into company-wise service template. Accelerated deployment \& slashed new service launch cycle from 10 days to 3 days.}
        \resumeItem{Scoped and decomposed major epics into clear deliverables, coordinating cross-functional teams of engineers, PMs, and international vendor partners to hit every go-to-market milestone.}
        \resumeItem{Mentored three interns and junior engineers through building production integration -- ran pairing sessions and established code-review standards to boost team velocity and code quality.}
      \resumeItemListEnd

    \resumeSubSubheading
      {\hspace{8px}Business \& Revenue Growth}
      \resumeItemListStart
        \resumeItem{Delivered various revenue-driving products—fintech financing solution, accounting integration, shipment security filing, and cargo tracking—which improved customer satisfaction and opened new upsell channels.}
        \resumeItem{Architected the API gateway \& Webhook mechanism as the vital interface for GoFreight's extension ecosystem, enabling integrations with large enterprises and partners via various plugins \& adapters.}
        \resumeItem{Stabilized and sunset the legacy payment platform, then led end-to-end development of a new payment solution, achieving more than a 10x uplift in transaction volume and revenue.}
      \resumeItemListEnd

    \resumeSubSubheading
      {\hspace{8px}Service Reliability \& Operational Efficiency}
      \resumeItemListStart
        \resumeItem{Partnered with DevOps to introduce Grafana dashboards and alerting on CloudWatch, Elasticsearch, and Snowflake sources, standardizing incident response playbooks and cutting manual monitoring duration by 5 hours per week.}
        \resumeItem{Built executive dashboards that accelerate metrics reporting by 80\% leveraging customized usage-collecting library, Snowflake, dbt, \& Metabase, providing real-time product adoption insights and enabling data-driven decisions.}
        \resumeItem{Automated onboarding/transition workflows with internal UI to reduce operational tasks and accelerate time-to- value for new integrations.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{Umbo Computer Vision} & \textit{Oct 2018 - Sep 2021} \\
      \multicolumn{2}{l}{\footnotesize UmboCV aims at revolutionizing the surveillance industry with cloud-based AI systems for detecting human or vehicle intrusion.} \\
    \end{tabular*}
    \vspace{0px}
    
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{Backend Engineer - Cloud AI Team} & \textit{} \\
    \end{tabular*}
      \vspace{0px}
      \resumeSubSubheading
        {\hspace{8px}CV Detection Services \& Per-Video-Channel Performance Monitoring}
        \resumeItemListStart
          \resumeItem{Developed multiple event-filtering logic based on motion value, deep-learning-model output mask analysis, and human-examining feedback. Raised system automate rate from 40\% to 90\% while sustaining 10x channel growth.}
          \resumeItem{Reconstructed event-based detection service from AWS Lambda to an HTTP server built on FastAPI \& AWS ECS.}
          \resumeItem{Improved server throughput by 20\% through serving with Gunicorn, handling I/O-bounded tasks asynchronously, and optimizing GIF generation, with metrics from load testing using \href{https://locust.io/}{Locust} as proof.}
          \resumeItem{Assembled cross-services latency tracing dashboards with the association of alerting mechanism by utilizing New Relic Tracing, providing end-to-end visibility into the multi-stage AI pipeline's performance.}
        \resumeItemListEnd

      \vspace{4px}
      \resumeSubSubheading
        {\hspace{8px}Human-in-the-Loop Service for Boosting Detection Accuracy}
        \resumeItemListStart
          \resumeItem{Solved scalability issues by revamping the human-interacting mechanism with AWS API Gateway for WebSocket.}
          \resumeItem{Enhanced filtration logic based on a time-weighted scoring algorithm that boosted overall automation rate by 8\% while achieving 98\% recall rate.}
          \resumeItem{Reduced average request latency by 30\% through MongoDB optimization, such as rectifying indexes to accommodate usage patterns, refining queries for index-covered query plans, \& adopting read-write separation.}
          \resumeItem{Implemented ETL cronjobs deployed to AWS EKS with Helm for importing event metadata to Elasticsearch, which powers the customer usage analysis and system healthiness monitoring.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

  \pagebreak

  % %-----------Projects-----------------
  % \vspace{4px}
  % \section{Selected Projects} 
  %   \resumeSubHeadingListStart
  %     \vspace{-2pt}\item
  %     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
  %       \textbf{Poject A} & {}
  %     \end{tabular*} \vspace{-8px}

  %     \resumeItemListStart
  %       \resumeItem{item 1.}
  %     \resumeItemListEnd
  %   \resumeSubHeadingListEnd
 
  %   \vspace{-12px} 
  %   \resumeSubHeadingListStart
  %     \vspace{-2pt}\item
  %     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
  %       \textbf{Poject B} & {}
  %     \end{tabular*} \vspace{-8px}

  %     \resumeItemListStart
  %       \resumeItem{item 2.}
  %     \resumeItemListEnd
  %   \resumeSubHeadingListEnd 


  %-----------COMMUNITY-----------------
  \vspace{4px}
  \section{Open Source \& Community Experience} 
    \resumeSubHeadingListStart
      \vspace{-2pt}\item
      \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{Python Documentation Community} & {} \\
        \textit{Event Host \& Contributor} & \textit{July 2021 - Present} 
      \end{tabular*} \vspace{-8px}
      \resumeItemListStart
        \resumeItem{Led volunteers to grow 
          \href{https://github.com/python/python-docs-zh-tw}{Python official document's Traditional Chinese translation} coverage from 2\% to
          \href{https://python-docs-translations.github.io/dashboard/}{$\sim$40\%}, and improved contributor efficiency by automating translation workflows and standardizing terminology.}
        \resumeItem{Hosted monthly Python doc translation meetups with accumulated \textgreater200 participants in the past 3 years, and organized translation workshops at conferences such as
          \href{https://tw.pycon.org/2024/zh-hant/events/sprints/}{PyCon TW},
          \href{https://coscup.org/2024/zh-TW/session/ZKLYAZ}{COSCUP},
          \href{https://conf2024.sciwork.dev/projects}{sciwork}, etc.
        }
        \resumeItem{Contributed improvements to the docs of various Python projects
          (\href{https://github.com/python/cpython/issues?q=(involves\%3Amattwang44\%20OR\%20author\%3Amattwang44)\%20AND\%20label\%3Adocs}{\textit{CPython}},
          \href{https://github.com/fastapi/fastapi/issues?q=(involves\%3Amattwang44\%20OR\%20author\%3Amattwang44)\%20AND\%20label\%3Alang-zh-hant}{\textit{FastAPI}},
          etc.) and \href{https://github.com/sphinx-contrib/sphinx-lint/issues?q=involves\%3Amattwang44}{\textit{sphinx-lint}}.
        }
        \resumeItem{Co-organized CPython contribution workshop, facilitated participants through code build and setup processes.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

    \vspace{-12px} 
    \resumeSubHeadingListStart
      \vspace{-2pt}\item
      \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{PyCon Taiwan} & {} \\
        \textit{Dev Lead \& Mentor} & \textit{Mar 2020 - Oct 2023}
      \end{tabular*} \vspace{-8px}

      \resumeItemListStart
        \resumeItem{Led a team of 10+ volunteer developers to maintain the \href{https://tw.pycon.org}{2021-2023 official website} and \href{https://github.com/pycontw/pycon.tw/issues?q=involves\%3Amattwang44}{the proposal submission/ reviewing platform in Django}.}
        \resumeItem{Rebuilt \href{https://github.com/pycontw/pycontw-frontend/issues?q=involves\%3Amattwang44+OR+author\%3Amattwang44}{the frontend from scratch in Nuxt.js} to replace the old Django templates for lower development and maintenance cost and better support of SEO and i18n.}
        \resumeItem{Administrated the GCP infrastructure for dev teams (web, data, and automation) and managed cost structure.}
        \resumeItem{Coached successor leaders on cross-functional collaboration, stakeholder communication, and project management.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd 

    \vspace{-12px}
    \resumeSubHeadingListStart
      \vspace{-2pt}\item
      \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{Django Community} & {} \\
        \textit{Contributor} & \textit{2023 - Present}
      \end{tabular*} \vspace{-8px}
      \resumeItemListStart
        \resumeItem{Contributed to Django projects such as
          \href{https://github.com/model-bakers/model_bakery/issues?q=involves\%3Amattwang44}{model\_bakery},
          \href{https://github.com/hardcoretech/data-spec-validator/issues?q=involves\%3Amattwang44}{data-spec-validator},
          \href{https://github.com/yychen/dj-registry/issues?q=involves\%3Amattwang44+}{dj-registry}, and
          \href{https://github.com/django/django-localflavor/issues?q=involves\%3Amattwang44}{django-localflavor}.
        }
      \resumeItemListEnd
    \resumeSubHeadingListEnd

  %--------TECHNICAL SKILLS------------
  \vspace{4px}
  \section{Technical Skills}
    \begin{itemize}[leftmargin=*, label={}]
      \vspace{-1pt}\item{
        \textbf{Languages}{: Python, JavaScript (TypeScript)} \\
        \textbf{Web Development}{: Django, FastAPI, Flask, Express.js (Node.js), Vue.js/Nuxt.js, TailwindCSS} \\
        \textbf{Cloud Services}{: AWS (EC2, S3, ECS, SQS, Lambda, API Gateway), GCP} \\
        \textbf{Databases}{: MySQL, MongoDB, Redis} \\
        \textbf{CI/CD \& IaC}{: Terraform, Serverless, GitHub Actions, ArgoCD, Jenkins, TravisCI} \\
        \textbf{Logging \& Monitoring}{: Grafana, Elastic Stack, New Relic} \\
        \textbf{Data Engineering}{: dbt, Snowflake, BigQuery, Metabase} \\
      }
    \end{itemize}

  %-----------CERTIFICATE-----------------
  \vspace{4px}
  \section{Selected Certificates}
    \begin{itemize}[leftmargin=*, label={}]
      \vspace{-1pt}
      \item
        \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
          \href{https://learn.mongodb.com/c/dYiWu0OfSK2lF6bHyY-XPA}
          {\textbf{MongoDB Certified Associate Data Modeler}}
          & \textit{\small Mar 2024} 
        \end{tabular*}

        \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
          \href{https://www.credly.com/badges/a09b790c-0152-4008-97c9-2ca8265eafb6}
          {\textbf{AWS Certified Solutions Architect - Associate}}
          & \textit{\small Aug 2023} 
        \end{tabular*}

        % TODO: Delete this in my next update. It's too old.
        \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
          \href{https://www.credential.net/f9e5b522-87ec-4e3e-bf3e-d65d4e760d1c}
          {\textbf{Redis Certified Developer}}
          & \textit{\small Nov 2021} 
        \end{tabular*}

        \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
          \href{https://www.credly.com/badges/adcca0d4-b53f-4829-92b5-8262c53049f5}
          {\textbf{HashiCorp Certified: Terraform Associate}}
          & \textit{\small Nov 2021} 
        \end{tabular*}

        \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
          \href{https://www.credly.com/badges/10809727-c851-4095-ab4b-04719c519441}
          {\textbf{Astronomer Certification for Apache Airflow Fundamentals}}
          & \textit{\small Nov 2021} 
        \end{tabular*}

        \vspace{2pt}
        \item\small{%
          \href{https://www.linkedin.com/in/weihsiang-wang/details/certifications/}{\textbf{See additional certifications and course works on my LinkedIn.}}%
        }

    \end{itemize}

    %-----------EDUCATION-----------------
    \vspace{4px}
    \section{Education}
      \begin{itemize}[leftmargin=*, label={}]
        \vspace{-1pt}\item
          \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
            \textbf{National Taiwan University} & \\
            \textit{\small B.S. \& M.S., Mechanical Engineering (Research Topic: Mechanism Design \& Patent Analysis)} & \textit{\small Aug 2012 - Aug 2018} \\
          \end{tabular*}\vspace{-5pt}
      \end{itemize}

  %-------------------------------------------
\end{document}